NOSQL\\ BEST PRACTICES

### 2018-03-28 pgconfus2018/presentation.tex
More slides and examples

@@

@@

>>>>

        \begin{itemize}[label={\MVRightarrow}]
            \item Plain Json
            \item Binary Jsonb
            \item Relation
        \end{itemize}

        \includegraphics[width=0.75\textwidth,center]{json_vs_jsonb.png}

        \includegraphics[width=0.75\textwidth,center]{jsonb_vs_relation.png}

@@

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Types, please}

@@

    \vspace{1cm}
    \begin{tikzpicture}
        \draw[line width=0.5mm] (0,0) rectangle (2,1) node[pos=.5] {};
        \draw[line width=0.5mm] (2,0) rectangle (4,1) node[pos=.5] {};
        \draw[line width=0.5mm] (4,0) rectangle (6,1) node[pos=.5] {};
        \draw[line width=0.5mm, fill=red!30] (6,0) rectangle (8,1) node[pos=.5] {DIFF};
        \draw[line width=0.5mm] (8,0) rectangle (10,1) node[pos=.5] {};
        \draw[line width=0.5mm] (10,0) rectangle (12,1) node[pos=.5] {};
        \draw[->, line width=1mm, dashed] (0,-0.5) -- (6,-0.5);
        \draw[<-, line width=1mm, dashed] (8,-0.5) -- (12,-0.5);
    \end{tikzpicture}

    \begin{tikzpicture}
        \draw[line width=0.5mm] (0,0) rectangle (2,1) node[pos=.5] {\{};
        \draw[line width=0.5mm, fill=red!30] (2,0) rectangle (4,1) node[pos=.5] {DIFF};
        \draw[line width=0.5mm, fill=red!30] (4,0) rectangle (6,1) node[pos=.5] {};
        \draw[line width=0.5mm, fill=red!30] (6,0) rectangle (8,1) node[pos=.5] {};
        \draw[line width=0.5mm, fill=red!30] (8,0) rectangle (10,1) node[pos=.5] {DIFF};
        \draw[line width=0.5mm] (10,0) rectangle (12,1) node[pos=.5] {\}};
        \draw[->, line width=1mm, dashed] (0,-0.5) -- (2,-0.5);
        \draw[<-, line width=1mm, dashed] (10,-0.5) -- (12,-0.5);
    \end{tikzpicture}

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Huge documents}

        \begin{itemize}[label={\MVRightarrow}]
            \item TOAST has significant overhead (assemble, locks)
            \item Other than that ~ linear degradation
        \end{itemize}

        \includegraphics[width=0.7\textwidth,center]{document_size.png}

\begin{frame}
    \frametitle{}
    \begin{center}
    \textbf{Alignment}

    \begin{itemize}[label={}]
        \item Variable-length portion is aligned to a 4-byte
        \item \inputminted[fontsize=\Large]{sql}{sql/insert_align1.sql}
        \item \begin{figure}
            \includegraphics[width=0.58\textwidth,left]{align_short.png}
        \end{figure}

        \item \inputminted[fontsize=\Large]{sql}{sql/insert_align2.sql}
        \item \begin{figure}
            \includegraphics[width=0.75\textwidth,left]{align_long.png}
        \end{figure}

    \end{itemize}

\fontsize{13pt}{14}\selectfont
\section{Extensions}
\fontsize{17pt}{18}\selectfont

\begin{frame}
    \frametitle{}
    \begin{center}
        \textbf{Why to write an extension?}

        \vspace{1cm}
        \begin{itemize}[label={\MVRightarrow}]
            \item Implement some convenient functionality\\ (e.g. jsonb intersection)
            \item Create function optimized for your domain model
        \end{itemize}

\begin{frame}
    \frametitle{}
    \begin{center}
        \textbf{Why to write an extension?}

        \vspace{1cm}
        \begin{flushleft}
            findJsonbValueFromContainer -> binary search

            \_id in a fixed position?
        \end{flushleft}

        \begin{itemize}[label={\MVRightarrow}]
            \item Raw Jsonb container when search for an element
            \item Iterate through JsonbValue when update
        \end{itemize}

\begin{frame}
    \frametitle{}
    \begin{center}
        \textbf{Reuse infrastructure}

        \begin{itemize}[label={\MVRightarrow}]
            \item findJsonbValueFromContainer
            \item JsonbIterator
            \item addToParseState
            \item worker functions
        \end{itemize}

\begin{frame}
    \frametitle{}
    \begin{center}
        \textbf{Random tips}

        \begin{itemize}[label={\MVRightarrow}]
            \item Clone iterator
            \item String are not null-terminated
        \end{itemize}
